A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2021-11-22 sections/abstract/main.tex
Add changes suggested by guide for authors
- Add abstract
- Add acknowledgements
- Fix the title page
- Change bibliogrpahy style
Minor changes based on subsequent review
- Changes in title page (addresses)
- Changes in abstract
- Changes in acknowledgements

\begin{abstract}
The focus of this research is the construction of a 3-player game theoretic 
model between two queueing systems and a service that distributes individuals 
to them. 
The resultant model will then be used to explore dynamics between all players.
The first aspect of this work is the development of a queueing system with two
consecutive waiting spaces. 
The strategic managerial behaviour corresponds to how individuals use these 
waiting spaces. 
Two modelling techniques were used: discrete event simulation and Markov chains.
The state probabilities of the Markov chain system have been used to extract 
the performance measures of the queueing model (e.g. mean time in each waiting
room, mean number of individuals in each room, etc.).
A 3-player game theoretic model is proposed between the two queueing systems
and the service that distributes individuals to them.
In particular this can be seen as a 2-player normal-form game where the 
utilities are determined by a third player with its own strategies and 
objectives. 
A backwards induction technique is used to get the utilities of the normal-form
game between the two queueing systems.
This particular system can be applied in a healthcare scenario where it 
captures the emergent behaviour between, for example, the Emergency Medical 
Service (EMS) and the Emergency Department (ED). 
This will be used to investigate the impact of target measures on patient 
well-being.
\end{abstract}

>>>>

\begin{abstract}
This research describes the development and application of a 3-player game 
theoretic model between two queueing systems and a service that distributes 
individuals to them. 
The resultant model is used to explore dynamics between all players.
The first aspect of this work is the development of a queueing system with two
consecutive waiting spaces where
the strategic managerial behaviour corresponds to how individuals use these 
waiting spaces. 
Two modelling techniques are deployed: discrete event simulation and Markov 
chains.
The state probabilities of the Markov chain system are used to extract 
the performance measures of the queueing model (e.g. mean time in each waiting
room, mean number of individuals in each room, etc.).
A 3-player game theoretic model is subsequently proposed between the two 
queueing systems and the service that distributes individuals to them.
In particular this can be viewed as a 2-player normal-form game where the 
utilities are determined by a third player with its own strategies and 
objectives. 
A backwards induction technique is used to get the utilities of the normal-form
game between the two queueing systems.
This particular system has many applications, including those in healthcare
where it captures the emergent behaviour between the Emergency Medical 
Service (EMS) and the Emergency Department (ED). 
The impact of time-target measures on patient well-being is explored in this 
paper.
\end{abstract}

\begin{keyword}
    Game theory \sep Queueing theory \sep OR in healthcare
\end{keyword}

### 2021-11-22 title.tex
Make changes based on spellchecker
- Update known words
- Fix a minor typo
Minor changes based on subsequent review
- Changes in title page (addresses)
- Changes in abstract
- Changes in acknowledgements

\title{A game theoretic model of the behavioural gaming that takes place at the 
EMS - ED interface\tnoteref{t1}}
\tnotetext[t1]{This document is the results of the research project funded by 
the heathcare improvement studies institute.}

@@

\author[2]{Vince Knight}
\ead{knightva@cardiff.ac.uk}

\author[3]{Paul Harper}
\ead{harper@cardiff.ac.uk}

\address[1]{The Abacws 2.67, Senghennydd Rd, Cardiff CF24 4AX, United Kingdom}
\address[2]{The Abacws 2.52, Senghennydd Rd, Cardiff CF24 4AX, United Kingdom}
\address[3]{The Abacws 2.56, Senghennydd Rd, Cardiff CF24 4AX, United Kingdom}

>>>>

\title{A game theoretic model of the behavioural gaming that takes place at the 
EMS - ED interface\tnoteref{t1}}
\tnotetext[t1]{This document is the results of the research project funded by 
the healthcare improvement studies institute.}

@@

\author[1]{Vince Knight}
\ead{knightva@cardiff.ac.uk}

\author[1]{Paul Harper}
\ead{harper@cardiff.ac.uk}

\address[1]{School of Mathematics, Cardiff University, Cardiff CF24 4AX, United Kingdom}
